Behavior-driven development (BDD) is claimed to originate from an
article written by \citet{web:dan_north}, and is based on
TDD \cite{wiki:bdd}. This section is based upon the original article
written by \citeauthor{web:dan_north}.\\

\citeauthor{web:dan_north} describes that several confusions and
misunderstandings often appeared when he taught TDD and other agile
practices in projects. Programmers had trouble to understand what to
test and what not to test, how much to test at the same time, naming
their tests and understanding why their tests failed.
\citeauthor{web:dan_north} thought that it must be possible to introduce
TDD in a way that avoids these confusions.\\

Instead of focusing on what test cases to write for a specific feature,
BDD instead focuses on behaviors that the feature should imply. Each
test is described by a sentence, typically starting with the word
\emph{should}. For a function calculating the number of days left until
a given date, this could for example be \quotes{should return 1 if
tomorrow is given} or \quotes{should raise an exception if the date is
in the past}.\\

Many frameworks use strings for declaring the sentence describing each
test. Using strings rather than traditional function names allows us to
use a native language, and solves the problem of naming tests. The
string describing the behavior is used instead of a traditional function
name, which also makes it possible to give a human-readable error if the
module fails to fulfill some behavior. This can make it easier to
understand why a test fails. It also sets a natural barrier for how
large the test should be, since it must be possible to describe in one
sentence.\\

After coming up with these ideas, \citeauthor{web:dan_north} met a
software analyst and realized that writing behavior-oriented
descriptions about a system had much in common with software analysis.
Software analysts write specifications and acceptance criteria for
systems before development, which are used when developing the system as
well as for evaluating the system during acceptance testing. They came
up with a way of writing scenarios in order to represent the purpose and
preconditions for behaviors in a uniform way, as seen below.\\

\framebox[\textwidth]{
\minibox{
    \emph{Given} some initial context (the givens),\\
    \emph{When} an event occurs,\\
    \emph{Then} ensure some outcomes.\\
}}
\linebreak
\linebreak

By using this pattern, analysts, developers and testers can all use the
same language, and is hence called a \emph{ubiquitous language} (a
language that exists everywhere). Multiple scenarios are written by
analysts to specify the properties of the system, which can be used by
developers as functional requirements, and as desired behaviors when
writing tests.\\
