
The case study is divided into three sub parts. The purpose of each
sub part is to evaluate some aspects of the testing approach, in order
to compose a good evaluation of the chosen testing approach when
combined.\\


\subsection{Refactoring of old tests}

There have been attempts to introduce testing of the ECP system a while
back, but this has stopped since the chosen approaches was found to be
very cumbersome. At the start of this project, the implemented tests had
not been maintained for a very long time, which resulted in that many
tests failed although the system itself worked fine.\\

As mentioned in section \ref{sec:hypothesis}, TDD methodology is
used during the case study. This methodology is based on the fact that
tests are written before implementation of new features and then run
iteratively during development. The test suite should pass, then fail
after a new test has been implemented, and then pass again after the new
feature has been implemented. This of course presupposes that existing
tests can be run and give predictable results.\\

The first part of the case study is therefore to make all old tests run.
Apart from being a prerequisite for new tests and features to be
implemented, it also gives a view on how tests are affected as new
functionality is implemented. This is especially interesting since it
otherwise would be impossible to evaluate such factors in the scope of a
master's thesis. It also gives a perspective on some of the advantages
and drawbacks of the old testing approach.\\

Another drawback of the old tests are the fact that they run too slow in
order to be continuously in a TDD manner. Another objective of this part
of the case study is therefore to make them faster, so at least some of
the tests can be run continuously.\\


\subsection{Implementation of new functionality}

As mentioned in section \ref{sec:background}, the commissioner body of
this project wishes to implement support for staff manning in the ECP
system. This functionality is implemented and tests are written for
new parts of the system as well as for re-factored code.\\

The purpose of this part is, besides implementing the new feature
itself, to evaluate test-driven development and how tests and
implementation code can be written together by using TDD methodology and
an iterative development process. We also gain more experience of
writing unit tests in order to evaluate how different kinds of tests
serves different purposes in the development process.\\


\subsection{Increasing test coverage}

In order to evaluate the tests written in previous parts of the case
study, code coverage is used as a measure. The last part of the case
study focuses on analyzing parts of the application that is untested or
very weakly tested, and write tests for them. We also evaluate the tests
written in previous parts of the case study and complement them if
needed.\\

The purpose of this part is to get a more solid experience of using test
coverage as a measure for code quality, and to produce a measurable
output of the case study. We also look at how TDD methodology works in
an situation where the functionality is already implemented without
tests, as opposed to using it when implementing new functionality.\\
