% [Ska ge en bakgrund till problemet, motivera varför det är viktigt samt
% [beskriva det i detalj. Ska även beskriva förväntat resultat.
% [Problemformuleringen ska grundas i litteraturbasen. Planera för att
% [finjustera formuleringen i takt med att litteraturstudierna fortgår.]

In large organizations, there is often a need for efficient
administration of staff. Resource planning is often used to determine
the required production capacity in order to reach a specific goal. One
example could be the required number of examinations that is needed to
be done at a hospital in order to keep the waiting times within specific
bounds. The results of the resource planning poses as the base for
allocating staff. GOLI is a startup company developing a web application
for production planning, currently focused on following up plans and
goals. Due to requirements from customers, the code base will be
extended to include new features.\\

During code refactoring or implementation of new features in software,
errors often occur in existing parts. Automatic testing is often used to
verify the functionality of software, in order to detect bugs and errors
before they end up in a production environment. The goal of this
master's thesis is to analyze how this can be introduced in a good way,
and if lower-level tests can be derived from existing high-level tests
automatically.\\


\subsection{Formulation of question}

\begin{itemize}
    \item How can a combination of low-level and high-level testing be used
          in order to achieve good test coverage?
    \item Is it possible to automate the process of breaking down high-level
          behavioral into lower-level unit tests?
\end{itemize}


% The current product uses automatic testing to some extent, primary
% behavior-level testing in the Cucumber framework. According to the
% developers, these tests are cumbersome to write and takes long time to
% run.

