\MakeShortVerb{\|}

\quotes{Software is written by humans and therefore has bugs} [sic].
This quote was coined by John Jacobs \cite{web:quote_jacobs}, and
explains the basic reason for software testing. Most programmers would
agree that defects tend to show up during the software development
process as well as in the finished software. The ultimate goal of the
testing process is to establish that a certain level of software quality
has been reached, which is achieved by revealing defects in the code
\cite{book:adp}.\\

Automated software testing is typically performed by writing pieces of
code\footnote{There are also techniques for recoding clicks when testing
graphical interfaces, but that is not considered in this thesis.}
called \emph{tests} \cite{wiki:test_automation}. Each test uses the
implemented code that we want to evaluate, and performs different
assertions to make sure that the result is the same as we expect. Code
listing \ref{lst:basic_function} shows a very simple function and code
listing \ref{lst:dummy_test} shows a piece of code for testing it.\\

For writing more complicated tests, and in order to manage collections
of tests, writing a bunch of |if| statements for every test is
repetitive and tedious. Several languages provide |assert|
statements\footnote{The Ruby core module does not provide this as a
reserved word, but it is included as part of the Test::Unit module.},
which checks if the given condition is true, and raises an exception
otherwise -- the assertion \emph{fails}. The same test using assertions
is shown in code listing \ref{lst:basic_test}. However, we often want to
have more support than just statements like this. We may for example
want to run a piece of code before each test for a specific module,
assert that a function throws an exception, or present different error-
messages depending on the assertion. A \emph{testing
framework}\footnote{Also called testing tool.} typically provides such
functionality. \cite{wiki:test_automation}\\

The code for each test is executed by a \emph{test runner}, which in
many cases is included as a part of the testing framework. The test
runner finds and executes our collection of tests (called \emph{test
suite}), and then collects and reports the results back to the user. If
at least one assertion in a test fails during the execution, the test is
considered to have failed. A test may also fail due to syntax errors and
unexpected exceptions.\\


\begin{lstlisting}[caption=An example function.,
                   label=lst:basic_function, float=t]

def plus(x, y)
  return x + y
end

\end{lstlisting}


\begin{lstlisting}[caption=A piece of code that could be used for testing the function in code listing \ref{lst:basic_function}.,
                   label=lst:dummy_test, float=t]

def test_plus
  if !(plus(1, 2) == 3)
    raise
  end
  if !(plus(3, -4) < 0)
    raise
  end
end

\end{lstlisting}

\begin{lstlisting}[caption=A basic test for the function in code listing \ref{lst:basic_function}.,
                   label=lst:basic_test, float=t]

def test_plus
  assert plus(1, 2) == 3
  assert plus(3, -4) < 0
end

\end{lstlisting}
