During code refactoring or implementation of new features in software,
errors often occur in existing parts. This may have a serious impact on
the reliability of the system, thus jeopardizing user's confidence for
the system. Automatic testing is utilized to verify the functionality of
software in order to software defects before they end up in a production
environment.\\

Starting new web application companies often means rapid product
development in order to create the product itself, while maintenance
levels are low and the quality of the application is still easy to
assure by manual testing. As the application and the number of users
grow, maintenance and bug fixing becomes an increasing part of the
development. The size of the application might make it unlikely to
test in a satisfying way by manual testing.\\

The commissioner body of this project, GOLI, is a startup company that
is developing a web application for production planning called GOLI
Kapacitetsplanering. Due to requirements from customers, the company
wishes to extend the application to include new features for handling
staff manning. \\

The existing application uses automatic testing to some extent. The
developers however feel that these tests are cumbersome to write and
take long time to run. The purpose of this thesis is to analyze how
this application can begin using tests in a good way whilst the
application is still quite small. The goal is to determine a solid way
of implementing new features and bug fixes in order for the product to
be able to grow effortlessly.\\
