\MakeShortVerb{\|}

\subsection{Writing conventions}

Terms written in \emph{italics} are subjects that appear further on in
this thesis. Understanding the meaning of these may be required for
understanding concepts later on.\\


\subsection{Choices and definitions}

Code examples are written in Ruby\footnote{\url{https://www.ruby-
lang.org}} 2.1.1 since that is the primary language of this project. The
focus of the code examples is yet to be understandable by people without
knowledge of Ruby, rather than using Ruby-specific practices. For
example, implicit |return|-statements are avoided since these are
hard to understand for people used to languages without this feature,
such as Python or Java. Code examples typically originate from
implemented code, but names of classes and functions have been altered
for copyright, consistency and understandability reasons.\\

The built-in Ruby module Test::Unit is used for general test code
examples in order to preserve the independence of a specific testing
framework as far as possible, although other testing frameworks are also
mentioned and exemplified in this thesis. Another reason for this choice
is to avoid introducing unnecessary complexity for these examples.\\

The area of software development contains several terminologies that are
similar or exactly the same. In cases where multiple different
terminologies exist for a certain concept, we have chosen the term with
most hits on Google. The purpose of this was to choose the most widely-
used term, and the number of search results seemed like a good measure
for this. A footnote with alternative terminologies is present when
such terminology is defined.\\

The term \emph{testing} will in this thesis refer to automatic software
testing with the purpose of finding software defects, unless specified
otherwise. We will also refer to the GOLI Kapacitetsplanering software
as \emph{the application}. We will use the term \emph{test-driven
development methodologies} as a collective term for both test- and
behavioral driven development (explained in \fref{sec:tdd} and
\ref{sec:bdd}).\\
